Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-12-04 presentations/illustrations/presentation-illustrations.tex
adjusted the linear capability prevents attack 2 slides to fit directly with attack 2.

\begin{frame}
    \frametitle{Linear caps prevent attack 1}
  \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

    % Split the stack pointer
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw node[right=0cm of usp] { stack pointer };
      \draw node[right=0cm of sp2] { private stack pointer };
    \end{onlyenv}

    % Callee called
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw node[right=0cm of usp] { stack pointer };
      \draw node[fill=gray!50, right=0cm of sp2] { return data pointer };
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \actadv{(0,5)}{(6,8)}{callee stack frame}
    \end{onlyenv}

@@

    \begin{onlyenv}<+-.(2)>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw node[fill=gray!50, right=0cm of sp2] { return data pointer };

@@

    % At this point we have a linear point stored in a part of memory that it governs. In other words, no other capabilities can grant access to this part of memory, to the capabilitiy is essentially lost.
    \draw<+> node[teal,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (4,10) { Stack pointer\\essentially lost.};

    \begin{onlyenv}<+->
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw node[right=0cm of sp2] { return data pointer };

@@

      \begin{scope}
        \fill[fill=gray!50] (0,2.5) rectangle (6,15) node[pos=.5,color=black] {};
        \draw (0,0) -- (0,15);
        \draw (6,0) -- (6,15);
      \end{scope}
      \draw[fill=gray!50] (0,13) rectangle (6,13.5) node[pos=.5,color=red] {\footnotesize sp};
      \actsf{(0,2.5)}{(6,5)}{caller stack frame} 
  \end{onlyenv}

  \draw<+>[teal,very thick] (6.4,4.4) -- (7.4,5.4);
  \draw<.>[teal,very thick] (7.4,4.4) -- (6.4,5.4);
  \draw<.> node[teal,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (14,7) { Splice fails, no\\stack pointer returned.};

>>>>

\begin{frame}
    \frametitle{Linear caps prevent attack 1}
  \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart
    \draw (16.5,5.5) node {register file};
    \begin{scope}
      \clip (15.9,1.1) rectangle (17.1,5.1);
      \foreach \x in {1,2,...,4}
      {
        \draw[fill=white] (16,\x) rectangle (17,\x+1) node[pos=.5,color=teal] {};
      };
    \end{scope}
    \node (r1) at (16.75,4.5) {};
    \node (r2) at (16.75,3.5) {};

    % Caller 
    \actsf{(0,2.5)}{(6,5)}{caller stack frame} 
    \begin{onlyenv}<+>
      \capbrace[sp1]{(6.5,2.5)}{(6.5,16)}
      \draw node[right=0cm of sp1] { stack pointer };
      \draw (r1) edge[->,red,bend left] (sp1);
    \end{onlyenv}

    % Split the stack pointer
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw (r2) edge[->,red,bend left] (sp2);
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw (r1) edge[->,red,bend left] (usp);
      \draw node[right=0cm of usp] { stack pointer };
      \draw node[right=0cm of sp2] { private stack pointer };
    \end{onlyenv}

    % Callee called
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw (r2) edge[->,red,bend left] (sp2);
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw (r1) edge[->,red,bend left] (usp);
      \draw node[right=0cm of usp] { stack pointer };
      \draw node[fill=gray,opacity=0.5, right=0cm of sp2] { return data pointer };
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \actadv{(0,5)}{(6,8)}{callee stack frame}
    \end{onlyenv}

@@

    \begin{onlyenv}<+-.(1)>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw node[fill=gray!50, right=0cm of sp2] { return data pointer };

@@

    % At this point we have a linear point stored in a part of memory that it governs. In other words, no other capabilities can grant access to this part of memory, to the capabilitiy is essentially lost.
%    \draw<+> node[teal,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (4,10) { Stack pointer\\essentially lost.};

    \begin{onlyenv}<+->
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw node[fill=gray!50,right=0cm of sp2] { return data pointer };

@@

      \begin{scope}
        \fill[fill=gray!50] (0,2.5) rectangle (6,15) node[pos=.5,color=black] {};
        \draw (0,0) -- (0,15);
        \draw (6,0) -- (6,15);
      \end{scope}
      \draw[fill=gray!50] (0,13) rectangle (6,13.5) node[pos=.5,color=red] {\footnotesize sp};
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \inactadv{(0,5)}{(6,8)}{callee stack frame}
      \actsf{(0,8)}{(6,10.5)}{callee (2) stack frame} 
  \end{onlyenv}

  \draw<+>[teal,very thick] (-0.5,7.5) -- (6.5,11);
  \draw<.>[teal,very thick] (-0.5,11) -- (6.5,7.5);
  \draw<.> node[teal,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (14,7) { No stack pointer\\for callee (2)!};
